### 2020-03-23 4_metg.tex
Some fiddling with text.

Given that Task Bench permits the rapid exploration of a large space
of application scenarios, one question is how to characterize the
performance and efficiency of the systems under study. As noted
earlier, the overheads of the systems we consider vary by more than
five orders of magnitude, making it challenging to extract useful
information from weak and strong scaling runs.

>>>>

Since Task Bench permits rapid exploration of a large space
of application scenarios, one question is how to characterize the
performance and efficiency of systems under study. As noted
above, the overheads of the systems we consider vary by more than
five orders of magnitude, making it challenging to extract useful
information from weak and strong scaling runs.
